Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2018-12-19 paper/snakemajoranas.tex
updated figure and made some changes in discussion

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
Modulating the geometry of the normal ribbon solves the problems of gap softening and majorana length in an effective and controllable manner.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner phase diagram.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry, and experimental efforts are already on their way.
Apart from optimizing the geometry for gap and Majorana length, the same freedom of geometry we use can additionally be applied to ease experimental implementation.
Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
A systematic study of the effect of specific geometrical features would be interesting to study.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
Experimental verification, along with further study of the proposed system is required to see whether their omittance obscure the improvements in the model studied in this manuscript.

\comment{Outlook: how to cope with the complications.}

>>>>

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majorana's would be an interesting continuation.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.
